Data Specialization for a Staged Lambda Calculus

### 2014-11-07 paper/splitting.tex
wrote about functions

[FUNCTIONS]

>>>>

Function introduction has a \texttt{()} precomputation, since functions are already fully reduced in our semantics.
But since the body of a function may be multistage, splitting must continue into it.
The immediate result is a new function formed out of the stage \bbone\ part of the original body,
and the resumer is a new function formed out of the stage \bbtwo\ part of the original body.
It is the responsibility of the application site to save the precomputation of the function body
and then appropriately pass it to the resumer version of the function.
